Verifying Demonstrations

### 2017-11-16 contents-poster.tex
Changes "user's perspective" to "overview"
Adds line to protocol showing what's during and after

    \begin{greenblock}{Our approach: user's perspective}
      \begin{itemize}
        \item The organizer publishes the protest's manifesto, e.g.\ QR-code on 
          placard.
        \item Each protester has a smartphone with a protest app.
        \item Each protester scans the QR code with the app.
        \item The app communicates with other apps locally, e.g.\ ad-hoc network 
          or Bluetooth.
        \item The apps issues participation proofs to each other.
        \item Once there is an Internet connection, the proofs are submitted to 
          a blockchain.
        \item Anyone can verify the proofs on the blockchain and count the valid 
          ones.
      \end{itemize}
    \end{greenblock}

@@

    \begin{figure}
      \centering
      \begin{minipage}{\linewidth}
        \begin{align*}
          O\to \text{all}\colon & \text{manifesto} \\
          P\colon & cid\gets H(\text{manifesto}), \\
          & pid\gets PRF_{k_P}(cid) \\
          P\to W\colon & pid \\
          W\leftrightarrow P\colon & \text{perform distance bounding} \\
          W\colon & wid\gets PRF_{k_W}(pid), \\
          & wsig\gets PRF_{k_W}(wid, t_s, l) \\
          W\to P\colon & (wid, t_s, l, wsig) \\
          W\to S\colon & H(pid, wid, t_s, l, wsig) \\
          P\to S\colon & H(pid, wid, t_s, l, wsig) \\
          W\to S\colon & (pid, wid, t_s, l, wsig),\\
          & NIZK(wid = PRF_{k_W}(pid), \\
            & wsig = PRF_{k_W}(wid, t_s, l), \\
            & \exists sign(k_W)) \\
          P\to S\colon & (pid, wid, t_s, l, wsig),\\
          & NIZK(pid = PRF_{k_P}(cid), \exists sign(k_P))
        \end{align*}
      \end{minipage}
      \caption{%
        An overview of message exchanges.
        The organizer \(O\) broadcasts the manifesto.
        \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
        Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
      }%
      \label{Protocol}
    \end{figure}

>>>>

    \begin{greenblock}{Our approach: overview}
      \begin{itemize}
        \item The organizer publishes the protest's manifesto, e.g.\ QR-code on 
          placard.
        \item Each protester has a smartphone with a protest app.
        \item Each protester scans the QR code with the app.
        \item The app communicates with other apps locally, e.g.\ ad-hoc network 
          or Bluetooth.
        \item The apps issues participation proofs to each other.
        \item Once there is an Internet connection, the proofs are submitted to 
          a blockchain.
        \item Anyone can verify the proofs on the blockchain and count the valid 
          ones.
      \end{itemize}
    \end{greenblock}

@@

    \begin{figure}
      \centering
      \begin{minipage}{\linewidth}
        \begin{align*}
          O\to \text{all}\colon & \text{manifesto} \\
          P\colon & cid\gets H(\text{manifesto}), \\
          & pid\gets PRF_{k_P}(cid) \\
          P\to W\colon & pid \\
          W\leftrightarrow P\colon & \text{perform distance bounding} \\
          W\colon & wid\gets PRF_{k_W}(pid), \\
          & wsig\gets PRF_{k_W}(wid, t_s, l) \\
          W\to P\colon & (wid, t_s, l, wsig) \\[-1em]
          && \text{during} \\ \hline && \text{after} \\[-1em]
          W\to S\colon & H(pid, wid, t_s, l, wsig) \\
          P\to S\colon & H(pid, wid, t_s, l, wsig) \\
          W\to S\colon & (pid, wid, t_s, l, wsig),\\
          & NIZK(wid = PRF_{k_W}(pid), \\
            & wsig = PRF_{k_W}(wid, t_s, l), \\
            & \exists sign(k_W)) \\
          P\to S\colon & (pid, wid, t_s, l, wsig),\\
          & NIZK(pid = PRF_{k_P}(cid), \exists sign(k_P))
        \end{align*}
      \end{minipage}
      \caption{%
        An overview of message exchanges.
        The organizer \(O\) broadcasts the manifesto.
        \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
        Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
      }%
      \label{Protocol}
    \end{figure}
